\documentclass[../custom]{flashcards}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{float}

\newcommand{\studyArea}{Risk Management Applications of Derivatives}

\def\labelitemii{$\circ$}
\def\labelitemiii{$\diamond$}
\def\labelitemiv{$\cdot$}

\begin{document}
\cardfrontstyle{headings}
\cardfrontfoot{Study Session 15}

\begin{flashcard}[\studyArea]{Number of Equity Futures Contracts Needed for a Target Portfolio Beta}
    \begin{flushleft}
        The formula for beta of a particular asset is $a$ is
        \begin{align*}
            \beta_a &= \frac{\text{cov}(a, M)}{\sigma^2_M}\\
            \\
            \text{where:}\\
            \text{cov}(a, M) &= \text{covariance of returns on asset $a$ with the market}\\
            \sigma^2_M &= \text{variance of the market returns}
        \end{align*}
        The number of contracts needed to achieve target portfolio beta, $\beta_T$, is
        \begin{align*}
            \text{number of contracts} &= \left ( \frac{\beta_T - \beta_P}{\beta_f} \right ) \left ( \frac{V_P}{P_f \times \text{multiplier}} \right )\\
            \\
            \text{where:}\\
            \beta_T &= \text{desired portfolio beta}\\
            \beta_P &= \text{portfolio beta}\\
            \beta_f &= \text{equity futures contract beta}\\
            V_P &= \text{current value of the portfolio}\\
            P_f &= \text{futures price}
        \end{align*}
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Basic Form for Synthetic Equity or Synthetic Cash}
    \begin{flushleft}
        Synthetic cash or synthetic equity is modeled using long or short offsetting positions in equity futures.
        \begin{itemize}
            \item A synthetic risk-free asset is formed with a long stock position and a short stock index futures position.
            \item A synthetic equity position is formed with a long risk-free asset and a long stock index futures position.
        \end{itemize}
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Number of Equity Futures Contracts Needed for Synthetic Cash Position}
    \begin{flushleft}
        An equity position can be converted to a synthetic cash position for $T$ years by using
        \begin{align*}
            \text{number of equity contracts} &= - \frac{V_P (1 + R_F)^T}{P_f}\\
            \\
            \text{where:}\\
            V_P &= \text{value of the equity position}\\
            P_f &= \text{total futures price (quoted price times multiplier)}\\
            R_F &= \text{risk-free rate}\\
            T &= \text{designated period of time}
        \end{align*}
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Number of Futures Contracts Needed to Achieve for a Target Portfolio Duration}
    \begin{flushleft}
        \begin{align*}
            \text{number of contracts} &= (\text{yield beta}) \left ( \frac{\text{MD}_T - \text{MD}_P}{\text{MD}_F} \right ) \left ( \frac{V_P}{P_f \times \text{multiplier}} \right )\\
            \\
            \text{where:}\\
            V_P &= \text{current value of the portfolio}\\
            P_f &= \text{futures price}\\
            \text{MD}_T &= \text{target modified duration}\\
            \text{MD}_P &= \text{modified duration of the portfolio}\\
            \text{MD}_F &= \text{modified duration of the futures contract}
        \end{align*}
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Steps to Synthetically Change Equity and Bond Allocations}
    \begin{itemize}
        \item To reallocate from equity to bonds
            \begin{enumerate}
                \item Remove all systematic risk (target a beta of zero) by shorting equity futures.
                \item Add duration to the position (target a modified duration of more than zero) by going long bond futures.
            \end{enumerate}
        \item To reallocate from bonds to equity
            \begin{enumerate}
                \item Remove all duration (target a modified duration of zero) by shorting bond futures.
                \item Add systematic risk to the position (target a beta of more than zero) by going long equity futures.
            \end{enumerate}
    \end{itemize}
\end{flashcard}

\begin{flashcard}[\studyArea]{Preinvesting}
    \begin{flushleft}
        Preinvesting is taking a long futures position to create an exposure converting a future cash inflow into a synthetic equity or bond position.
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Three Types of Foreign Exchange Risk}
    \begin{enumerate}
        \item \textbf{Transaction exposure} is present when a cash flow in a foreign currency occurs at a future date. Can be hedged by selling forward in the case of a receipt or buying forward in the case of a payment.
        \item \textbf{Economic exposure} refers to situations when changes in currency value affect competitiveness. Some examples are companies that
            \begin{itemize}
                \item Export and sell products in foreign markets. Domestic currency appreciation means less competitive products internationally.
                \item Purchase and import from foreign markets. Domestic currency depreciation means costs in the domestic currency increase.
                \item Operate domestically, but have competitors or suppliers who are affected by changes in currency value.
            \end{itemize}
            This can be desirable to hedge, but difficult to quantify.
        \item \textbf{Translation exposure} is the risk of converting foreign financial statements into domestic currency units. Generally not hedged as it's not seen as a real cash flow risk.
    \end{enumerate}
\end{flashcard}

\begin{flashcard}[\studyArea]{Hedging Foreign Market and Foreign Currency Risks}
    \begin{itemize}
        \item Hedging foreign market risk
            \begin{itemize}
                \item Can sell short (sell forward) the foreign market index.
                \item The effectiveness depends on correlation of the portfolio and the market index. Perfect correlation will return the foreign risk-free rate.
                \item Applying a currency hedge on top of this will return the domestic risk-free rate.
            \end{itemize}
        \item Hedging foreign currency risk
            \begin{itemize}
                \item Problem is uncertainty of future value. Strategies to deal with this are
                \begin{itemize}
                    \item Hedge a minimum future value.
                    \item Hedge the estimated future value.
                    \item Hedge the initial value of the portfolio.
                \end{itemize}
            \end{itemize}
    \end{itemize}
\end{flashcard}

\begin{flashcard}[\studyArea]{Hedging with Forwards Versus Futures}
    \begin{itemize}
        \item Practical differences
            \begin{itemize}
                \item Futures are standardized while forwards are customized.
                \item Forwards have counterparty risk while futures use clearinghouses.
                \item Futures are more regulated and transparent.
                \item Futures require margin.
            \end{itemize}
        \item Empirical differences
            \begin{itemize}
                \item Most bond and equity hedging is done with futures, but this creates cross-hedge and basis risk.
                \item Interest payment and currency hedges usually use forwards so exact amounts and dates can be hedged.
                \item Eurodollar futures are a large market that is mostly used by dealers and market makers to hedge their own business needs.
            \end{itemize}
    \end{itemize}
\end{flashcard}

\begin{flashcard}[\studyArea]{Covered Call}
    \begin{flushleft}
        Buy the underlying and sell a call option. Used to generate income when the underlying price is expected to remain unchanged.
        \begin{center}
            \begin{tikzpicture}
                \draw[<->] (0, -1.5) -- (0, 3) node[above] {Profit};
                \draw[->] (0, 0) node[left] {\$0} -- (8, 0) node[right] {Stock Price};
                \draw[dashed] (0, 0.5) -- (3, 0.5) -- (5, -1) node[right] {written call};
                \draw[ultra thick] (1, -1) -- (3, 0.5) -- (6, 0.5) node[right] {covered call};
                \draw (1.75, -1) -- (6.25, 2.375) node[above right] {stock};
            \end{tikzpicture}
        \end{center}
        \begin{align*}
            \text{profit} &= -\max(0, S_T - X) + S_T - S_0 + C_0\\
            \text{maximum profit} &= X + C_0 - S_0\\
            \text{maximum loss} &= S_0 - C_0\\
            \text{breakeven price} &= S_0 - C_0
        \end{align*}
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Protective Put}
    \begin{flushleft}
        Buy the underlying and buy a put option. Limits downside risk at the cost of the put premium, $P_0$.
        \begin{center}
            \begin{tikzpicture}
                \draw[<->] (0, -1.5) -- (0, 3) node[above] {Profit};
                \draw[->] (0, 0) node[left] {\$0} -- (8, 0) node[right] {Stock Price};
                \draw[dashed] (1, 1.75) -- (4, -0.5) -- (7, -0.5) node[right] {long put};
                \draw[ultra thick] (0, -0.5) -- (4, -0.5) -- (7, 1.75) node[right] {protective put};
                \draw (2.75, -1) -- (7.25, 2.375) node[above right] {stock};
                \node[below] at (4, -0.5) {$X$};
                \draw[fill] (4.75, 0) circle[radius=1.5pt] node[below right] {$S_0 + P_0$};
            \end{tikzpicture}
        \end{center}
        \begin{align*}
            \text{profit} &= \max(0, X - S_T) + S_T - S_0 - P_0\\
            \text{maximum profit} &= S_T - S_0 - P_0\\
            \text{maximum loss} &= S_0 - X + P_0\\
            \text{breakeven price} &= S_0 + P_0
        \end{align*}
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Bull Spread}
    \begin{flushleft}
        Purchase a call option with a low exercise price, $X_L$ and sell a call with a higher exercise price, $X_H$. At inception, $X_L < X_H$ and $C_{L, 0} < C_{H, 0}$. The investor expects the stock price to end up between $X_L$ and $X_H$. This provides limited upside if the stock rises, with a limited downside.
        \begin{center}
            \begin{tikzpicture}
                \draw[<->] (0, -1.5) -- (0, 3) node[above] {Profit};
                \draw[->] (0, 0) node[left] {\$0} -- (8, 0) node[right] {Stock Price};
                \draw[dashed] (0, -1) -- (2, -1) -- (6, 2) node[above right] {long call at $X_L$};
                \draw[ultra thick] (0, -0.5) -- (2, -0.5) -- (4, 1) -- (6, 1) node[right] {bull call spread};
                \draw (0, 0.5) -- (4, 0.5) -- (6, -1) node[below right] {short call at $X_H$};
                \draw (2, 0.1) -- (2, 0) node [above] {$X_L$} -- (2, -0.1);
                \draw (4, 0.1) -- (4, -0.1) node[below] {$X_H$};
            \end{tikzpicture}
        \end{center}
        \begin{align*}
            \text{profit} &= \max(0, S_T - X_L) - \max(0, S_T - X_H) - C_{L, 0} + C_{H, 0}\\
            \text{maximum profit} &= X_H - X_L - C_{L, 0} + C_{H, 0}\\
            \text{maximum loss} &= C_{L, 0} - C_{H, 0}\\
            \text{breakeven price} &= X_L + C_{L, 0} - C_{H, 0}
        \end{align*}
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Bear Spread}
    \begin{flushleft}
        Sell a call with a low exercise price, $X_L$ and buy a call with a higher exercise price, $X_H$. This provides limited upside if the stock falls, with a limited downside. As prices fall, the investor keeps the premium of the written call, net of the long call premium.
        \begin{center}
            \begin{tikzpicture}
                \draw[<->] (0, -2) -- (0, 2.5) node[above] {Profit};
                \draw[->] (0, 0) node[left] {\$0} -- (8, 0) node[right] {Stock Price};
                \draw[dashed] (0, 1) -- (2, 1) -- (6, -2) node[right] {short call at $X_L$};
                \draw[ultra thick] (0, 0.5) -- (2, 0.5) -- (4, -1) -- (6, -1) node[right] {bear call spread};
                \draw (0, -0.5) -- (4, -0.5) -- (6, 1) node[above right] {long call at $X_H$};
                \draw (2, 0.1) -- (2, -.03) node [below] {$X_L$} -- (2, -0.1);
                \draw (4, 0.1) -- (4, 0) node[above] {$X_H$} -- (4, -0.1);
            \end{tikzpicture}
        \end{center}
        \begin{align*}
            \text{profit} &= \max(0, S_T - X_H) - \max(0, S_T - X_L) + C_{L, 0} - C_{H, 0}\\
            \text{maximum profit} &= X_H - X_L + C_{L, 0} - C_{H, 0}\\
            \text{maximum loss} &= C_{L, 0} - C_{H, 0}\\
            \text{breakeven price} &= X_L + C_{L, 0} - C_{H, 0}
        \end{align*}
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Butterfly Spread with Calls}
    \begin{flushleft}
        Buy two calls at strike prices $X_L$ and $X_H$ and write two calls at strike price $X_M$ with $X_L < X_M < X_H$. The investor expects the stock price to stay near $X_M$, but the downside loss is limited by the purchased calls.
        \begin{center}
            \begin{tikzpicture}
                \draw[<->] (0, -2) -- (0, 2.5) node[above] {Profit};
                \draw[->] (0, 0) node[left] {\$0} -- (8, 0) node[right] {Stock Price};
                \draw[dashed] (0, -0.25) -- (4.5, -0.25) -- (6, 0.875) node[above right] {long call at $X_H$};
                \draw[dashed] (0, -0.75) -- (1.5, -0.75) -- (4.5, 1.5) node[above right] {long call at $X_L$};
                \draw[ultra thick] (0, -0.5) -- (1.5, -0.5) -- (3, 0.625) -- (4.5, -0.5) -- (6, -0.5) node[right] {long butterfly spread};
                \draw (0, 0.25) -- (3, 0.25) -- (6, -2) node[right] {short calls at $X_M$};
            \end{tikzpicture}
        \end{center}
        \begin{align*}
            \text{profit} &= \max(0, S_T - X_L) - 2 \max(0, S_T - X_M)\\
            &+ \max(0, S_T - X_H) - C_{L, 0} + 2C_{M, 0} - C_{H, 0}\\
            \text{maximum profit} &= X_M - X_L - C_{L, 0} + 2C_{M, 0} - C_{H, 0}\\
            \text{maximum loss} &= C_{L, 0} - 2 C_{M, 0} + C_{H, 0}\\
            \text{breakeven price} &= X_L + C_{L, 0} - 2C_{M, 0} + C_{H, 0} \text{ and } 2X_M - X_L - C_{L, 0} + 2C_{M, 0} - C_{H, 0}\\
        \end{align*}
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Straddle}
    \begin{flushleft}
        Buy both a put and a call with the same strike price and expiration on the same asset. The investor expects a large price move in some direction, and will incur a loss if the price remains static.
        \begin{center}
            \begin{tikzpicture}
                \draw[<->] (0, -2) -- (0, 2.5) node[above] {Profit};
                \draw[->] (0, 0) node[left] {\$0} -- (8, 0) node[right] {Stock Price};
                \draw[dashed] (0.25, 1.8125) -- (3, -0.25) -- (6, -0.25) node[right] {long put};
                \draw (0, -0.5) -- (3, -0.5) -- (5.75, 1.5625) node[above right] {long call};
                \draw[ultra thick] (0.25, 1.0625) -- (3, -1) -- (5.75, 1.0625) node[right] {long straddle};
            \end{tikzpicture}
        \end{center}
        \begin{align*}
            \text{profit} &= \max(0, S_T - X) + \max(0, X - S_T) - C_0 - P_0\\
            \text{maximum profit} &= S_T - X - C_0 - P_0\\
            \text{maximum loss} &= C_0 + P_0\\
            \text{breakeven price} &= X - C_0 - P_0 \text{ and } X + C_0 + P_0
        \end{align*}
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Collar}
    \begin{flushleft}
        Combination of a protective put and a covered call. Can be zero-cost if call and put premia are equal. Usually put has lower strike $X_L$ and call has higher strike $X_H$. Both the upside and downside are limited by the call and the put respectively.
        \begin{center}
            \begin{tikzpicture}
                \draw[<->] (0, -2.5) -- (0, 2) node[above] {Profit};
                \draw[->] (0, 0) node[left] {\$0} -- (8, 0) node[right] {Stock Price};
                \draw[dashed] (0.25, 0.8125) -- (2, -0.5) -- (6, -0.5) node[right] {long put};
                \draw (0, 0.25) -- (4, 0.25) -- (6, -1.25) node[right] {short call};
                \draw[ultra thick] (0, -0.75) -- (2, -0.75) -- (4, 0.75) -- (6, 0.75) node[right] {collar};
                \draw (0.25, -1.8125) -- (5, 1.75) node[right] {stock};
            \end{tikzpicture}
        \end{center}
        \begin{align*}
            \text{profit} &= \max(0, X_L - S_T) - \max(0, S_T - X_H) + S_T - S_0\\
            \text{maximum profit} &= X_H - S_0\\
            \text{maximum loss} &= S_0 - X_L\\
            \text{breakeven price} &= S_0
        \end{align*}
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Box Spread}
    \begin{flushleft}
        Combination of a bull call spread and a bear put spread. That is, a long call and short put at $X_L$ and a long put and a short call at $X_H$. The payoff is always the same, regardless of the underlying price, which means assuming the prices are correct, the payoff is the risk-free rate.
        \begin{center}
            \begin{tikzpicture}
                \draw[<->] (0, -2) -- (0, 2.5) node[above] {Profit};
                \draw[->] (0, 0) node[left] {\$0} -- (8, 0) node[right] {Stock Price};
                \draw[dashed] (0, 1) -- (2, 1) -- (4, -0.5) -- (6, -0.5) node[above, right] {bear put spread};
                \draw (0, -0.5) -- (2, -0.5) -- (4, 1) -- (6, 1) node[above, right] {bull call spread};
                \draw[ultra thick] (0, 0.25) -- (6, 0.25) node[below, right] {box spread};
                \draw[dotted] (2, -1.5) node[below] {$X_L$} -- (2, 1);
                \draw[dotted] (4, -1.5) node[below] {$X_H$} -- (4, 1);
            \end{tikzpicture}
        \end{center}
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Payoff of Interest Rate Calls and Puts}
    \begin{flushleft}
        The payoff for an interest rate call is
        \[
            \text{payoff} = \text{NP} \times \max(0, \text{LIBOR} - \text{strike rate}) \times (D / 360)
        \]
        where $NP$ is the notional principal and $D$ is the days in the theoretical underlying.

        The payoff for an interest rate put is
        \[
            \text{payoff} = \text{NP} \times \max(0, \text{strike rate} - \text{LIBOR}) \times (D / 360)
        \]
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Interest Rate Caps and Floors}
    \begin{flushleft}
        Interest rate caps and floors are series of interest rate call and put options. Each cap and floor is called a caplet and floorlet.\newline

        Caps and floors are OTC contracts so they're tailored. The terms generally specify
        \begin{itemize}
            \item Reference rate---typically LIBOR.
            \item Cap or floor strike rate.
            \item Length of the agreement.
            \item Length of the agreement ($D$).
            \item Notional principal ($\text{NP}$).
        \end{itemize}
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Considerations for Delta Hedging}
    \begin{itemize}
        \item Delta is only an approximation and is less accurate for larger changes in the stock price.
        \item Delta changes as market conditions change, including changes in $\Delta S$.
        \item Delta changes over time independent of other changes.
        \item In the Black-Scholes equation, $N(d_1)$ approximates delta.
    \end{itemize}
\end{flashcard}

\begin{flashcard}[\studyArea]{Effects of Gamma on Delta Hedging}
    \begin{flushleft}
        The greater the value of gamma the more risk in the position (i.e., the more variability in the value of the option.)\newline

        The gamma of an at-the-money option is greatest near the expiration. When gamma is large, option values are subject to large changes the position faces the most risk and the investor is most likely to use a two-option hedge. In this situation, two options are used to force both delta and gamma to zero.
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Duration of Interest Rate Swaps}
    \begin{itemize}
        \item For fixed-rate instruments, duration will be highest as interest rate changes will change the PV of cash flows.
        \item Floating-rate instruments have duration close to zero as future cash flows vary with interest rates.
        \item Floating-rate instruments can have non-zero duration if the next payment is set, e.g. with swaps. The convention is to treat the duration of the floating-rate side of a swap as half of the reset period.
        \item For a pay-floating swap, the duration is
        \[
            D_{\text{pay floating}} = D_{\text{fixed}} - D_{\text{floating}} > 0
        \]
    \end{itemize}
\end{flashcard}

\begin{flashcard}[\studyArea]{Effect of Interest Rate Swaps on Cash Flow Risk}
    \begin{flushleft}
        Entering into a fixed-payer swap reduces cash flow risk because future floating-rate payments are converted to certain fixed payments. However, this converts the low-duration floating payments to high-duration fixed payments. As a result, interest rates now affect the market value of the liability.
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Swap Notional Principal Needed for a Target Portfolio Duration}
    \begin{flushleft}
        The duration of a portfolio with a swap position is
        \begin{align*}
            V_P \cdot \text{MD}_T &= V_P \cdot \text{MD}_P + \text{NP} \cdot \text{MD}_{\text{swap}}\\
            \\
            \text{where:}\\
            V_P &= \text{original value of the portfolio}\\
            \text{MD}_i &= \text{modified duration}\\
            \text{NP} &= \text{notional principal of the swap}
        \end{align*}
        Usually the maturity of the swap is set, which fixes $\text{MD}_{\text{swap}}$, so solving for $\text{NP}$ gives
        \[
            \text{NP} = V_P \left ( \frac{\text{MD}_T - \text{MD}_P}{\text{MD}_{\text{swap}}} \right )
        \]
        This is a variation of the basic hedging formula set up to notional principal rather than number of contracts.
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Conversion of Foreign Cash Receipts into Domestic Cash Receipts}
    \begin{flushleft}
        Dealers will use contracts to create currency swaps which do not require exchange of principal. This is essentially a series of exchange-rate purchases in the future at a fixed exchange rate. The amounts exchanged are a function of the current exchange rate and the interest rate of the countries involved.
        \begin{enumerate}
            \item Divide the foreign cash flow received by the foreign interest rate to get the foreign-denominated NP. This is the foreign NP that would have produced the foreign cash flow at the given exchange rate.
            \item Using the current exchange rate, convert the foreign NP into the corresponding domestic NP.
            \item Enter the swap with this NP.
            \begin{enumerate}
                \item Pay the foreign cash flows received on the assets, and receive the equivalent domestic amount.
                \item The amount of each domestic cash flow is determined by the domestic interest rate times the domestic NP.
            \end{enumerate}
        \end{enumerate}
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Risks of Equity Swaps}
    \begin{itemize}
        \item Counterparty risk if the swap dealer is unable to make payments.
        \item Basis risk if the return on the stock portfolio doesn't exactly match the index payments made to the swap dealer.
            \item Cash flow risk in that the firm must have cash on hand in the event of a netted payment. This risk wouldn't exist had the firm sold stock and bought fixed-rate securities.
    \end{itemize}
\end{flashcard}

\begin{flashcard}[\studyArea]{Swaps for International Diversification}
    \begin{flushleft}
        Swaps can be used to create international diversification by paying the return on a domestic index and receiving the return on an international index. This creates extra cash flow compared to a fixed-receiver swap because of the possibility of both indices declining and having to make two payments.\newline

        Benefits of using these swaps are
        \begin{itemize}
            \item Costs are generally lower than selling domestic and buying international stock.
            \item Can be defined for a temporary period of time for which exposure is desired.
            \item Can be paid in U.S. dollars to avoid foreign currency exposure.
        \end{itemize}
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Use Swaps to Change Allocations}
    \begin{flushleft}
        Swaps can be used to synthetically change portfolio allocation. E.g., to allocate more heavily to large-cap stocks in a small-cap portfolio, a manager can enter into a swap paying the small-cap return and receiving the large-cap return.\newline

        This can also be used for bond portfolios to, e.g., reallocate from high- to low-grade bonds. This is different that an interest rate swap because of the total return aspect.
    \end{flushleft}
\end{flashcard}

\begin{flashcard}[\studyArea]{Payer and Receiver Swaptions}
    \begin{itemize}
        \item \textbf{Payer swaption.}
            \begin{itemize}
                \item Gives the buyer the right to be the fixed-rate payer in a prespecified swap at a prespecified date. Similar to a protective put in that it allows payment of a fixed-rate, even if rates have increased.
                \item If interest rates rise enough at expiration such that the new SFR is above the swaption SFR, the holder will exercise the swaption. The swaption swap has positive value.
                \item If interest rates fall so that the new SFR is below the swaption SFR, the holder will let the swaption expire. The swaption swap has negative value.
                \item Can be used to convert a future floating-rate loan into a fixed-rate loan.
            \end{itemize}
            \item \textbf{Receiver swaption.}
                \begin{itemize}
                    \item Gives the buyer the right to be the fixed-rate receiver in a prespecified swap at a prespecified date. The holder expects rates to fall, and the swap pays a higher fixed rate while paying a lower floating rate.
                    \item If interest rates move high enough and the new SFR is above the swaption SFR, the holder will let the swaption expire. The swap has negative value.
                    \item If interest rates fall and the new SFR is below the swaption SFR, the holder will exercise the swaption. The swap has positive value.
                    \item Can be used to convert a future fixed-rate loan to a floating-rate loan.
                \end{itemize}
    \end{itemize}
\end{flashcard}
\end{document}
